JD-R Theory: Using the Content of the O*Net

### 2022-08-18 SIOP2023/SIOP_PROCESS.Rmd
number formatting in table (2 decimals forced)

Component <- c("Constant", "Hindrance (X)", "Resource (W)", "Hindrance x Resource")
coeff <- round(results[c(2:5),1],2)
SE    <- round(results[c(2:5),2],2)
t     <- round(results[c(2:5),3],2)
p     <- round(results[c(2:5),4],2)

>>>>

Component <- c("Constant", "Hindrance (X)", "Resource (W)", "Hindrance x Resource")
coeff <- format(round(results[c(2:5),1],2), nsmall=2)
SE    <- format(round(results[c(2:5),2],2), nsmall=2)
t     <- format(round(results[c(2:5),3],2), nsmall=2)
p     <- format(round(results[c(2:5),4],2), nsmall=2)
